Behavior Driven Development in Haskell

### 2012-06-02 paper.tex
Fix typo
BCP: adapt code

\begin{quote}
\small
\begin{verbatim}
module Fib where
-- | Calculate Fibonacci numbers.
--
-- >>> fib 10
-- 55
fib :: Int -> Integer
fib = const 55
\end{verbatim}
\end{quote}

@@

main = hspec $ do
  describe "fib" $ do
    it "calculates arbitrary Fibonacci numbers" $ do
      property $ \(Small n) ->
        fib n == fib (n + 2) - fib (n + 1)
\end{verbatim}
\end{quote}

@@

So far, so good.  We have an implementaion of the Fibonacci function
that swiftly calculates correct values for all non-negative integers.
But what about negative ones? Let's assume that we want our
implementation to throw an exception in this case. We would
specify it like this.

>>>>

\begin{quote}
\small
\begin{verbatim}
-- | Calculate Fibonacci numbers.
--
-- >>> fib 10
-- 55
fib :: Int -> Integer
fib = const 55
\end{verbatim}
\end{quote}

@@

main = hspec spec

spec = do
  describe "fib" $ do
    it "calculates arbitrary Fibonacci numbers" $ do
      property $ \(Small n) ->
        fib n == fib (n + 2) - fib (n + 1)
\end{verbatim}
\end{quote}

@@

So far, so good.  We have an implementation of the Fibonacci function
that swiftly calculates correct values for all non-negative integers.
But what about negative ones? Let's assume that we want our
implementation to throw an exception in this case. We would
specify it like this.
